Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-11 paper/paper.tex
typo
assumptions about the noise

@@

One of these assumptions, for example, is that the true stellar
spectrum is constant with time; that is, the variations from
epoch-to-epoch are from noise or nuisances (like telluric absorption).
This assumption is critical and deep.
The entire edifice of extreme-precision \RV\ is built on this assumption:
With imperfect models of stellar structure and photospheres, it is
impossible to know the \emph{absolute} \RV\ of a star to high precision;
we satisfy ourselves that we can measure \emph{relative} velocities
to arbitrarily high precision.
Relative precision---and everything in this paper---depends on our
ability to measure shifts from epoch to epoch.
If the stellar spectrum is permitted (or observed) to change from epoch
to epoch, there is no fundamental way to determine or confirm spectral
shifts corresponding to Doppler shifts.
That is, even relative \RV\ measurements depend on a constancy of the
stellar spectrum.
This is a deep issue, extending far beyond the scope of this paper.
time-variable stellar spectra are not killing to the extreme-precision
\RV\ program!
But at current practices they may be limiting precision,
and to ameliorate their effects will require substantial and non-trivial adjustments to the
\foreign{status quo}.
We hope to address these in future work.

>>>>

% This file is part of the EPRV project.
% Copyright 2017, 2018 the authors.

% Style notes
% - Re-define acronyms in each section? So less flippy flippy?

@@

One of these assumptions, for example, is that the true stellar
spectrum is constant with time; that is, the variations from
epoch-to-epoch are from noise or nuisances (like telluric absorption).
This assumption is critical and deep.
The entire edifice of extreme-precision \RV\ is built on this assumption:
With imperfect models of stellar structure and photospheres, it is
impossible to know the \emph{absolute} \RV\ of a star to high precision;
we satisfy ourselves that we can measure \emph{relative} velocities
to arbitrarily high precision.
Relative precision---and everything in this paper---depends on our
ability to measure shifts from epoch to epoch.
If the stellar spectrum is permitted (or observed) to change from epoch
to epoch, there is no fundamental way to determine or confirm spectral
shifts corresponding to Doppler shifts.
That is, even relative \RV\ measurements depend on a constancy of the
stellar spectrum.
This is a deep issue, extending far beyond the scope of this paper.
Time-variable stellar spectra are not killing to the extreme-precision
\RV\ program!
But at current practices they may be limiting precision,
and to ameliorate their effects will require substantial and non-trivial adjustments to the
\foreign{status quo}.
We hope to address these in future work.

We also assumed that the noise is zero-mean, Gaussian, and with known
variance tensor.
There are certainly sources of noise that might violate these
assumptions.
There are two ways in which we might weaken our assumptions about
the noise.
The first is that the total noise acting on the system---and recall
that noise for us is anything not accounted for in our model of the
data---might not be Gaussian in form.
This will happen if the photon counts (per pixel) get low.
But it can also happen if there are unmodeled calibration artifacts
that don't happen to have Gaussian-distributed amplitudes.
This is not a problem in principle with computing or saturating the
information-theory limit (\CRLB).
The only significant change is that the simple Gaussian likelihood must
be replaced with the appropriate function.
That change modifies the \CRLB\ calculation, and it also modifies the
relevant data-analysis method, since cross-correlation (justified in
\sectionname~\ref{s:methods}) is only appropriate when the noise is
close to Gaussian.
In a non-Gaussian world, the \RV\ estimation must proceed by explicit
optimization of the likelihood (or Bayesian methods derived therefrom).

The second way in which we might weaken our assumptions about the
noise is that there might be contributions to the noise (especially
those coming from unmodeled calibration artifacts) with unknown
variance.
That is, it is an optimistic assumption that we know the variance of
the noise, and all the covariances.
Our only comment about this problem is that, at least, the assumption
is testable:
It is possible with big observing programs to look at the empirical
properties of the residuals away from the best-fit model.
Do the residuals appear to have zero mean and reasonable empirical
variance, given the assumed variance?
These tests are like chi-squared tests; they test the completeness
of the model.
If the model is incomplete, it can be fixed by adding new components
to the model (calibration vectors of various kinds, for example) or
inflating estimates of noise variance. Or both.
